Learning Discrete Bayesian Networks from Continuous Data

### 2016-08-09 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
minor

\begin{table}[ht]
	\centering
	\caption{
		Discretization results for several datasets.
    The number of samples, number of variables, network structure, and mean cross-validated log-likelihood under each discretization method are given.
    The Bayesian method consitently has highest likelihood.
	}
  \resizebox{\textwidth}{!}{
	 \input{Table3_2.tex}
  }
	\label{table:more_data_set}
\end{table}

@@

The methods developed in this paper increase the accuracy of Bayesian networks learned on datasets with continuous and mixed variables.
An automated process for simultaneously constructing Bayesian networks and discretization policies is appealing because of the potential to significantly reduce development time and cost when developing models for uncertainty and causality.

>>>>

\begin{table}[ht]
	\centering
	\caption{
		Discretization results for several datasets.
    The number of samples, number of variables, network structure, and mean cross-validated log-likelihood under each discretization method are given.
    The Bayesian method consitently has higher likelihood.
	}
  \resizebox{\textwidth}{!}{
	 \input{Table3_2.tex}
  }
	\label{table:more_data_set}
\end{table}

@@

% The methods developed in this paper increase the accuracy of Bayesian networks learned on datasets with continuous and mixed variables.
% An automated process for simultaneously constructing Bayesian networks and discretization policies is appealing because of the potential to significantly reduce development time and cost when developing models for uncertainty and causality.
